### 2022-10-05 tikz/bayes-rdm.tex
changes made; need to update letter to reviewers

    \node [block, label={[]225:{\footnotesize (d)}}] at (-4, 3) (models) {
            Multiple models\\
            $\vb{M} = \qty{M_1, \ldots, M_K}$\\
            for $p(\Omega | M_k)$
        };
    \node [block, label={[]225:{\footnotesize (a)}}] (decisions) at (0, 3) {
            Candidate decisions\\
            $\vb{x} = \qty{x_1, x_2, \ldots, x_I}$
        };
    \node [block, label={[]225:{\footnotesize (b)}}] at (-4, 0) (simulations) {
            Many possible futures\\
            $\vb{s}=\qty{s_1, \ldots, s_J}$\\
            where $s_j \in \Omega$
        };
    \path [line] (models) -- (simulations);
    \node [function, label={[]45:{\footnotesize (c)}}] (model) at (0, 0) {
            System model\\
            $u_{ij} = f(x_i, s_j)$
        };
    \path [line] (simulations) -- (model);
    \path [line] (decisions) -- (model);

    \node [derived, label={[]0:{\footnotesize (f)}}] (weights) at (0, -3) {
            Weights\\
            $\vb{w} = \qty{w_1, \ldots, w_J}$\\
            where $w_j \in (0, 1)$
        };
    \path [line] (simulations) -- (weights);

>>>>

    \node [block, label={[]225:{\footnotesize (d)}}] at (-4, 3) (models) {
            Probabilistic scenarios\\
            $\vb{M} = \qty{M_1, \ldots, M_K}$\\
            for $p(s | M_k)$
        };
    \node [block, label={[]225:{\footnotesize (a)}}] (decisions) at (0, 3) {
            Candidate decisions\\
            $\vb{x} = \qty{x_1, x_2, \ldots, x_I}$
        };
    \node [block, label={[]225:{\footnotesize (b)}}] at (-4, 0) (simulations) {
            Many possible futures\\
            $\vb{s}=\qty{s_1, \ldots, s_J}$\\
            where $s_j \in \Omega$
        };
    \path [line] (models) -- (simulations);
    \node [function, label={[]45:{\footnotesize (c)}}] (model) at (0, 0) {
            System model\\
            $u_{ij} = f(x_i, s_j)$
        };
    \path [line] (simulations) -- (model);
    \path [line] (decisions) -- (model);

    \node [derived, label={[]0:{\footnotesize (f)}}] (weights) at (0, -3) {
            Weights\\
            $\vb{w} = \qty{w_1, \ldots, w_J}$\\
            where $\sum_{j=1}^J w_j = 1$
        };
    \path [line] (simulations) -- (weights);
